Asymmetric SAM

### 2021-08-11 website/index.Rmd
Updates website

For more details, see @campitelli2021.

@@

Campitelli, E., Diaz, L., & Vera, C. (2021). Assessment of zonally symmetric and asymmetric components of the Southern Annular Mode using a novel approach. Climate Dynamics, (under review).

@@

```
@article{campitelli2021,
  title = {Assessment of Zonally Symmetric and Asymmetric Components of the {{Southern Annular Mode}} Using a Novel Approach},
  author = {Campitelli, Elio and Diaz, Leandro and Vera, Carolina},
  year = {2021},
  volume = {(under review)},
  journal = {Climate Dynamics}
}
```

>>>>

For more details, see @campitelli2021 and [the companion blog post](https://eliocamp.github.io/scrapbook/posts/2021-08-09-asymsam/).

@@

Campitelli, E., Díaz, L. B., & Vera, C. (2021). Assessment of zonally symmetric and asymmetric components of the Southern Annular Mode using a novel approach. Climate Dynamics. https://doi.org/10.1007/s00382-021-05896-5

@@

```
@article{campitelli2021,
  title = {Assessment of Zonally Symmetric and Asymmetric Components of the {{Southern Annular Mode}} Using a Novel Approach},
  author = {Campitelli, Elio and Díaz, Leandro B. and Vera, Carolina},
  date = {2021-08-09},
  journaltitle = {Climate Dynamics},
  shortjournal = {Clim Dyn},
  issn = {1432-0894},
  doi = {10.1007/s00382-021-05896-5},
  url = {https://doi.org/10.1007/s00382-021-05896-5}
}
